\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% ---------------- CUSTOM COMMANDS ----------------
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubheading}[4]{%
\vspace{-2pt}\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textbf{\small #2} \\
\textit{\small #3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% ---------------- DOCUMENT ----------------
\begin{document}

%----------HEADING----------
\begin{center}
{\Huge \scshape Blessing Edmund Kwame Dogbe} \\ \vspace{3pt}
Accra, Ghana $\cdot$ \faPhone~+233 536064409 $\cdot$
\href{mailto:dogbeblessingkwame@gmail.com}{\faEnvelope~dogbeblessingkwame@gmail.com} $\cdot$
\href{https://linkedin.com/in/edmund-blessing}{\faLinkedin~linkedin.com/in/edmund-blessing} $\cdot$
\href{https://github.com/GeekKwame}{\faGithub~github.com/GeekKwame} $\cdot$
\href{https://devedmund.vercel.app/}{\faGlobe~Portfolio}
\end{center}

%-----------PROFILE-----------
\section{Profile}
\small{
Full Stack Developer specializing in building scalable, modern web applications using \textbf{React, TypeScript, Django, and Python}. Strong background in Applied Mathematics, bringing analytical thinking and systematic problem-solving to software development. Experienced in real-time applications, AI integration, payment processing, RESTful API design, and delivering user-focused digital solutions with measurable business impact. Passionate about clean code, continuous learning, and contributing to innovative projects.
}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Kwame Nkrumah University of Science and Technology (KNUST)}{Jan 2021 -- Aug 2024}
{BSc in Applied Mathematics}{Kumasi, Ghana}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\small{
\textbf{Languages:} Python, JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL \\ 
\textbf{Frameworks \& Libraries:} Django, Django REST Framework, React, React Router, Node.js, Express, Tailwind CSS, Flask, Syncfusion \\ 
\textbf{Databases:} MySQL, SQLite, Supabase, Relational Database Design \\ 
\textbf{Real-time \& APIs:} WebRTC, Stream.io, RESTful APIs, Third-party API Integration, Google Gemini AI \\ 
\textbf{Payment \& Services:} Stripe, Supabase Authentication \\ 
\textbf{Tools:} Git, GitHub, Postman, VS Code, Chrome DevTools, npm/yarn, Docker \\ 
\textbf{Concepts:} Full-Stack Development, Authentication, AI Integration, Payment Processing, Data Analysis, Software Testing, Web Scraping \\ 
\textbf{Deployment:} Vercel, Netlify, PythonAnywhere
}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{The Tourist's Planner (Full Stack)}{2025}
{React Router v7, TypeScript, Tailwind CSS, Syncfusion, Supabase, Gemini AI, Stripe}{Personal Project}
\resumeItemListStart
\resumeItem{Built a comprehensive full-stack travel application combining AI-powered trip planning with seamless booking experience using Google Gemini AI.}
\resumeItem{Implemented role-based portals for tourists (My Trips, Booking) and admins (Dashboard, Trip Management) with React Router v7 navigation.}
\resumeItem{Integrated Stripe payment processing for secure transaction handling and Supabase for authentication and database management.}
\resumeItem{Designed responsive UI using Syncfusion components and Tailwind CSS, delivering modern and intuitive user experience.}
\resumeItemListEnd

\resumeSubheading
{Live Audio Room (Full Stack)}{2025}
{React, TypeScript, Stream.io, Node.js, Express, WebRTC}{Personal Project}
\resumeItemListStart
\resumeItem{Built a modern, real-time audio room application enabling live audio conversations similar to Clubhouse or Twitter Spaces.}
\resumeItem{Implemented real-time audio streaming using Stream.io Video SDK and WebRTC for seamless participant interactions.}
\resumeItem{Developed participant management and permission system with user authentication and session persistence.}
\resumeItem{Created a beautiful glassmorphism-inspired UI with responsive design and smooth user experience.}
\resumeItemListEnd

\resumeSubheading
{Book Website (Full Stack)}{2025}
{React (Vite), Django REST Framework, Python}{Personal Project}
\resumeItemListStart
\resumeItem{Built a full-stack book tracking web application with complete CRUD functionality using React and Django REST Framework.}
\resumeItem{Implemented RESTful API endpoints for creating, listing, updating, and deleting books with proper HTTP methods.}
\resumeItem{Designed a modern dark, glassmorphism-inspired UI with responsive layout and immersive background styling.}
\resumeItem{Configured CORS for secure frontend-backend communication and wrote basic automated tests for API behaviors.}
\resumeItemListEnd

\resumeSubheading
{Notes Application (Full Stack)}{2025}
{React, Django REST Framework, Python}{Portfolio Project}
\resumeItemListStart
\resumeItem{Developed a full-stack notes application with CRUD functionality using React and Django REST Framework.}
\resumeItem{Implemented RESTful APIs for note management with clean separation of frontend and backend concerns.}
\resumeItem{Built a responsive, dark-themed UI with auto-save functionality and real-time update behavior.}
\resumeItem{Focused on scalability, maintainable code structure, and intuitive user experience.}
\resumeItemListEnd

\resumeSubheading
{Indeed Job Scraper}{2024}
{Python, BrightData API}{Personal Project}
\resumeItemListStart
\resumeItem{Built a Python-based automation tool to collect job listings from Indeed using BrightData API.}
\resumeItem{Performed data cleaning, structured results, and exported datasets to CSV for analysis.}
\resumeItemListEnd

\resumeSubheading
{Movie Recommendation System}{2024}
{Python, Pandas, Scikit-learn, Streamlit}{Academic Project}
\resumeItemListStart
\resumeItem{Designed a recommendation engine using similarity-based machine learning techniques.}
\resumeItem{Deployed an interactive web interface with Streamlit for real-time recommendations.}
\resumeItemListEnd

\resumeSubheading
{Speech Emotion Recognition System}{2024}
{Python, Keras, Librosa}{Machine Learning Project}
\resumeItemListStart
\resumeItem{Developed a real-time emotion classification system using audio signal processing and deep learning.}
\resumeItem{Extracted MFCCs, Zero Crossing Rate, Energy, and Pitch features for emotion prediction.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Kwame Nkrumah University of Science and Technology (UITS)}{Oct 2024 -- Sep 2025}
{Information Technology Technician}{Kumasi, Ghana}
\resumeItemListStart
\resumeItem{Provided technical support for faculty and students, troubleshooting hardware, software, and network issues.}
\resumeItem{Maintained IT infrastructure, ensuring system reliability and minimal downtime across departments.}
\resumeItem{Assisted with network administration and system maintenance to support university operations.}
\resumeItemListEnd

\resumeSubheading
{M365Connect}{Dec 2024 -- Mar 2025}
{Python Developer (Backend) -- Intern (Remote)}{Germany}
\resumeItemListStart
\resumeItem{Developed backend services using Django, focusing on scalable REST API design and implementation.}
\resumeItem{Integrated third-party services and implemented automated web scraping solutions for data collection.}
\resumeItem{Worked on database optimization and backend performance improvements to enhance system efficiency.}
\resumeItem{Contributed to building robust backend infrastructure supporting multiple client requirements.}
\resumeItemListEnd

\resumeSubheading
{HubbleMind}{Nov 2024 -- Dec 2024}
{Data Science Intern (Remote)}{India}
\resumeItemListStart
\resumeItem{Preprocessed health datasets using encoding techniques (label encoding, one-hot encoding), outlier treatment with IQR, and feature engineering.}
\resumeItem{Built machine learning models for obesity level prediction and evaluated model performance metrics.}
\resumeItem{Conducted comprehensive data preprocessing including duplicate removal and feature selection for improved model accuracy.}
\resumeItemListEnd

\resumeSubheading
{Zidio Development}{Aug 2024 -- Nov 2024}
{Data Science Intern (Remote)}{India}
\resumeItemListStart
\resumeItem{Developed machine learning models for speech emotion recognition and recommendation systems.}
\resumeItem{Applied audio signal processing techniques (MFCCs, Zero Crossing Rate, Energy, Pitch) and collaborative filtering methods.}
\resumeItem{Deployed real-time emotion classification systems using deep learning frameworks.}
\resumeItemListEnd

\resumeSubheading
{Lerato Consult}{Nov 2022 -- Dec 2024}
{OS Technician \& IT Support Assistant}{Accra, Ghana}
\resumeItemListStart
\resumeItem{Installed, configured, and maintained Point of Sale (POS) systems for retail and hospitality clients.}
\resumeItem{Provided on-site technical support, reducing system downtime and improving client satisfaction.}
\resumeItem{Managed hardware and software installations, ensuring optimal performance for business operations.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}
\item \textbf{Learn React} - Scrimba (\href{https://coursera.org/share/ce783141a4dcbbe32990b2b21ab63ea8}{View Certificate})
 \item \textbf{The Full Stack} - Meta (\href{https://coursera.org/share/19541a26ae104d66db8cfc78accfed1a}{View Certificate})
 \item \textbf{APIs} - Meta (\href{https://coursera.org/share/67cd00c7798148805ba1a265d11cb719}{View Certificate})
 \item \textbf{Django Web Framework} - Meta (\href{https://coursera.org/share/a9ceefb50c30e1fae57f3363aac4797b}{View Certificate})
 \item \textbf{Databases for Backend Development} - Meta (\href{https://coursera.org/share/db187028aeb00281c5c4c499a7935461}{View Certificate})
 \item \textbf{Machine Learning With Python} - IBM (\href{https://coursera.org/share/889f0defc13b05fa370f87561e547991}{View Certificate})
 \item \textbf{System Administration and IT Infrastructure Services} - Google (\href{https://coursera.org/share/b3f928e0d724604cc613efa2dd1c5ce1}{View Certificate})
 \item \textbf{Deep Learning \& Neural Networks With Keras} - IBM (\href{https://coursera.org/share/d2b3b6971be0df66e0d781ce5dc76138}{View Certificate})
 \item \textbf{Version Control} - Meta (\href{https://coursera.org/share/07a5994a3aaacac12a80769e5e34724e}{View Certificate})
 \item \textbf{Programming in Python} - Meta (\href{https://coursera.org/share/887f1f4e2d8a308b89a4a3c0881a3071}{View Certificate})
 \item \textbf{Python for Data Science \& Machine Learning} - Udemy (\href{https://www.udemy.com/certificate/UC-d3b7ab94-2a92-4412-b528-6ec0ee078aa3/}{View Certificate})
\end{itemize}

\end{document}
